---
title: "Lab 3: Logistic Regression"
subtitle: "Princeton University"
author: "INSERT NAME"
output: 
  tufte::tufte_html:
    css: 
    tufte_variant: "envisioned"
    highlight: github-dark
    fig_height: 10
    fig_width: 14
    toc: true
    toc_depth: 1
execute: 
  message: false
  warning: false
format: 
  html:
    code-fold: false
    code-overflow: wrap
engine: knitr
---

-   If you are fitting a model, display the model output in a neatly formatted table. (The `gt` `tidy` and `kable` functions can help!). `Modelsummary` also looks good(https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html)

-   If you are creating a plot, use `ggplot` or `base`and make sure they are publication ready. That means there are clear labels for all axes, titles, etc.

-   Commit and push your work to GitHub regularly, at least after each exercise. Write short and informative commit messages.

-   When you're done, we should be able to knit the final version of the QMD in your GitHub as a HTML.

## Data: General Social Survey

The General Social Survey (GSS) has been used to measure trends in attitudes and behaviors in American society since 1972. In addition to collecting demographic information, the survey includes questions used to gauge attitudes about government spending priorities, confidence in institutions, lifestyle, and many other topics.

The data for this lab are from the 2016 General Social Survey. The original data set contains 2867 observations and 935 variables.

We will use and abbreviated data set that includes the following variables:

`natmass`: Respondent’s answer to the following prompt:

“We are faced with many problems in this country, none of which can be solved easily or inexpensively. I’m going to name some of these problems, and for each one I’d like you to tell me whether you think we’re spending too much money on it, too little money, or about the right amount…are we spending too much, too little, or about the right amount on mass transportation?”

`age`: Age in years.

`sex`: Sex recorded as male or female

`sei10`: Socioeconomic index from 0 to 100

`region`: Region where interview took place

`polviews`: Respondent’s answer to the following prompt:

“We hear a lot of talk these days about liberals and conservatives. I’m going to show you a seven-point scale on which the political views that people might hold are arranged from extremely liberal - point 1 - to extremely conservative - point 7. Where would you place yourself on this scale?”

The data are in gss2016.csv in the data folder.

```{r}
# packages should go here
```

## EDA

> Let’s begin by making a binary variable for respondents’ views on spending on mass transportation. Create a new variable that is equal to “1” if a respondent said spending on mass transportation is about right and “0” otherwise. Then plot the proportion of the response variable, using informative labels for each category.
>
> Use your skills to pretty up the plots with descriptive axis labels, perhaps a title, and adjust the colors and other settings in the plot themes. Do yourself proud.

```{r}
# load data

```

```{r}
# answer here
```

> Recode `polviews` so it is a factor with levels that are in an order that is consistent with question on the survey. Note how the categories are spelled in the data.

```{r}

```

> Make a plot of the distribution of `polviews`

```{r}
  
```

> Which political view occurs most frequently in this data set?

> Make a plot displaying the relationship between satisfaction with mass transportation spending and political views. Use the plot to describe the relationship the two variables.

```{r}
```

-   We’d like to use age as a quantitative variable in your model; however, it is currently a character data type because some observations are coded as "89 or older".

> Recode age so that is a numeric variable. Note: Before making the variable numeric, you will need to replace the values "89 or older" with a single value.

```{r}
```

> Plot the distribution of age.

```{r}
# plot age

```

## Logistic regression

> Let’s start by fitting a model with just the intercept

```{r}
#fit intercept-only

```

> Interpret the intercept in the context of the data. Convert the $\beta_0$ parameter out of the log-odds metric to the probability metric. Make sure to include the 95% confidence intervals. Then interpret the results in a sentence or two--what is the basic thing this probability tells us about?

-   

> Now let's fit a model using the demographic factors - `age`,`sex`, `sei10` - to predict the odds a person is satisfied with spending on mass transportation. Make any necessary adjustments to the variables so the intercept will have a meaningful interpretation. *Neatly display the model coefficients (do not display the summary output)*

```{r}
# fit model

```

> Consider the relationship between sex and one’s opinion about spending on mass transportation. Interpret the coefficient of sex in terms of the logs odds and OR of being satisfied with spending on mass transportation. What are the predicted probabilities for males and females on support for spending on mass transportation? Please include the 95% CIs around each estimate.

```{r}
#interpret sex

```

> Consider the relationship between age and one’s opinion about spending on mass transportation. Interpret the coefficient of age in terms of the logs odds and OR of being satisfied with spending on mass transportation. Please include the 95% CIs around each estimate.

```{r}
#interpret age

```

> Consider the relationship between SES and one’s opinion about spending on mass transportation. Interpret the coefficient of SES in terms of the logs odds and OR of being satisfied with spending on mass transportation. Please include the 95% CIs around each estimate.

```{r}
#interpret ses

```

## Marginal effects

-   Let's examine the results on the probability scale.

> Calculate the marginal effects of sex, age, and SES on mass transportation spending. You can use the `margins` package function `margins` discussed in your textbook or you can use the `marginaleffects` package `avg_slope` `avg_comparisons` discussed in lecture. Interpret each estimate.

```{r}


```

## Model comparison

-   Now let’s see whether a person’s political views has a significant impact on their odds of being satisfied with spending on mass transportation, after accounting for the demographic factors.

> Conduct likelihood ratio test to determine if `polviews` is a significant predictor of attitude towards spending on mass transportation. Name these two models `fit2` and `fit3`, respectively. Compare the two models.

```{r}


```

> Is the model with `polviews` better than the model without?

## Visualization

-   Let’s plot the results

-   Use your model to visualize:

    -   The relationship between one’s political views and their attitude towards spending on mass transportation

    -   The relationship between sex and attitude towards spending on mass transportation

    -   The relationship between SES and their attitude towards spending on mass transportation. https://solomonkurz.netlify.app/blog/2021-09-22-sexy-up-your-logistic-regression-model-with-logit-dotplots/ has a cool example to use

    ::: callout-tip
    -   adjust the various settings in your plot to make it look professional.

    -   You can use `ggeffects` to get the predicted probabilities for these models.
    :::

```{r}
#plot

```

## Model fit

> Calculate the $R^2$ for the final model

```{r}


```

> Is the logistic model a good choice for this data? Look at the binned residual plot to assess this.

```{r}


```

## Assumptions

-   Here I just want to you too look at the assumptions-no need to fix anything

> Is there any multicollinearity in the model?

```{r}
#check multicollinearity

```

> How about outliers?

```{r}

# check outliers

```

> The model fit is not the best. Take a look at the binned residual plots for each continuous predictor variable and look at the linearity. Is there a predictor that sticks out? What can we do to improve model fit in this case?

::: callout-tip
If you run the `binned_residuals` function from `easystats` it will print out a message letting you know :). You can plot the binned residuals for each predictor by using `binned_residuals(model, term="predictor") %>% plot(show_dots=TRUE)`
:::

```{r}

```

## Reporting

Let's put this all together in a write-up. Be sure your answer includes the interpretation of the model coefficients and associated hypothesis tests or confidence intervals used to support your response. Include a table of the results (using `modelsummary`) and figures highlighting significant effects. Make sure your write-up is in APA style and the figures and tables are publication-ready. I DO NOT WANT TO SEE REPORT SOELY BEING USED HERE.
